---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ⚤ name2sex

The goal of name2sex is to convert a vector of first names into sex estimates (female percent) based on historical data bases.

## NOTE

If you're reading this, I'd encourage you to check out https://github.com/ropensci/gender instead. In making this package, we made some decisions that are probably not completely obvious. So it'd be more transparent [and probably all-around better] to use the https://github.com/ropensci/genderdata and https://github.com/ropensci/gender packages directly!

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mkearney/name2sex")
```
## Example

This is a basic example:

```{r example}
## load package
library(name2sex)

## vector of first names
first_names <- c("casi", "mike", "tracy", "rory", "pat", "alex", "tamar")

## apply names2sex function to first names
names2sex(first_names)
```
